A perfect storm and the natural endowments of trade-enabling infrastructure

### 2023-07-18 Slides/10min/10min.Rmd
10 min version of slides

#### What will be demonstrated:
  - The channel caused trade 
  - The channel caused a local population boom
  - Mechanism
  - Evidence for the reverse natural experiment in 1100s

@@

---
# Litterature
.pull-left[
- History desribed by Poulsen (2019, 2022)
- Does infrastructure promote regional development? (Fogel, 1964; Bogart, 2009; Donaldson & Hornbeck, 2016; Berger & Enflo, 2017; etc.)
- Does trade cause growth? (Frankel & Romer, 1999; Feyrer, 2021; Pascali, 2017)
- Fundamental determinants of economic wealth: *Institutions or geography?* 
- Pragmatically: Infrastructure is expensive

@@

???
**15/45**

@@

---
![Event](Figures/Map.png)

---
name: str-presentation
# 1. Trade: Sound Toll Register (STR)

@@

# 2. Population: Census data

@@

![Ship traffic](Figures/Ship_trafic_channel.png)
*Descriptive statistics from Svalgaard (1977) sourced from customs archives*
---
# The channel caused trade

@@

---
# The channel caused trade
```{r echo=FALSE, out.width="100%", fig.align='center'}
knitr::include_graphics("Figures/STR_regressions - Copy.png")
```

@@

---
.pull-left[
**Fishing:**
```{r echo=FALSE, out.width="100%", fig.align='center'}
knitr::include_graphics("Figures/fish.png")
```

]
--
.pull-right[
**Manufacturing:**
```{r echo=FALSE, out.width="100%", fig.align='center'}
knitr::include_graphics("Figures/manu.png")
```

---
### Migration and fertility
.pull-left[
**People who live in different county than their birth county:**
```{r echo=FALSE, out.width="100%", fig.align='center'}
knitr::include_graphics("Figures/born_different.png")
```
]
--
.pull-right[
**Child/women ratio (ch. 1-5 years per f. 15-45):**
```{r echo=FALSE, out.width="100%", fig.align='center'}
knitr::include_graphics("Figures/fertility.png")
```

@@

>>>>

#### This paper
- The channel caused trade 
- The channel caused a local population boom
- Mechanism
- Evidence for the reverse natural experiment in 1100s

@@

**15/45**

---
# Litterature
.pull-left[
- History described by Poulsen (2019, 2022)
- Does infrastructure promote regional development? (Fogel, 1964; Bogart, 2009; Donaldson & Hornbeck, 2016; Berger & Enflo, 2017; etc.)
- Does trade cause growth? (Frankel & Romer, 1999; Feyrer, 2021; Pascali, 2017)
- Fundamental determinants of economic wealth: *Institutions or geography?* 
- Pragmatically: Infrastructure is expensive

@@

???

@@

@@

# Census data

@@

]
---
# The channel caused trade

@@

---
```{r echo=FALSE, out.width="100%", fig.align='center'}
knitr::include_graphics("Figures/STR_regressions - Copy.png")
```

@@

---
.pull-left[
**Fishing:**
```{r echo=FALSE, out.width="100%", fig.align='center'}
knitr::include_graphics("Figures/fish_MA.png")
```

**Manufacturing:**
```{r echo=FALSE, out.width="100%", fig.align='center'}
knitr::include_graphics("Figures/manu.png")
```

]
--
.pull-right[
**Fertility:**
```{r echo=FALSE, out.width="100%", fig.align='center'}
knitr::include_graphics("Figures/fertility.png")
```

**Reallocation:**
```{r echo=FALSE, out.width="100%", fig.align='center'}
knitr::include_graphics("Figures/born_different_share_MA.png")
```

@@

---
name: str-presentation
# Trade data: Sound Toll Register (STR)

![Ship traffic](Figures/Ship_trafic_channel.png)
*Descriptive statistics from Svalgaard (1977) sourced from customs archives*
